Lyman-alpha spectra from rotating outflows

### 2017-11-08 paper/paper.tex
paper updated

\newcommand{\HII}{{\text{H\MakeUppercase{\romannumeral 2}}} }
\newcommand{\cm}{\ifmmode{{\rm cm}}\else cm\fi}
\newcommand{\ccm}{\,\mathrm{cm}^{-3}}
\newcommand{\ergps}{\,{\rm erg}\,{\rm s}\ifmmode{}^{-1}\else ${}^{-1}$\fi}
\newcommand{\Mpch}{\,{\rm Mpc}\,\ifmmode h^{-1}\else $h^{-1}$\fi}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\vek}[1]{\bm{#1}}
\newcommand{\hb}{H$\beta$}
\newcommand{\ha}{H$\alpha$}
\newcommand{\oiii}{[OIII]}
\newcommand{\oii}{[OII]}
\newcommand{\nii}{[NII]}
\newcommand{\esca}{erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$}
\newcommand{\esc}{erg cm$^{-2}$ s$^{-1}$}
\newcommand{\es}{erg s$^{-1}$}
\newcommand{\esa}{erg s$^{-1}$}
\newcommand{\sigmaclump}{$54.3\pm 0.6$ km s$^{-1}$}
\newcommand{\inftyclump}{$54.3\pm 5.1$ km s$^{-1}$}
\newcommand{\probaclump}{$0.96\pm 0.01$}

@@

\begin{abstract}
We perform Monte Carlo radiative transfer simulations of outflowing
gas with additional solid body rotation.
We reproduce the main features of the outcoming spectra with a simple
semi-analytic model that modifies the spectra of outflows without
rotation by adding a Doppler shift with the rotational information.

>>>>

@@

\begin{abstract}
We perform Monte Carlo radiative transfer simulations of outflowing
gas with additional solid body rotation. We reproduce the main features 
of the outcoming \lya line spectra with a simple semi-analytic model 
that modifies the spectra of outflows without rotation by adding a 
Doppler shift with the rotational information.
